Towards Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-07-03 SWoPP2018 Paper/paper.tex
Updated the figure and changed the captions slightly.

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{training_overview.pdf}
  \caption{Overview over our framework, showing blocks existing (white) and components currently worked on (gray)}\label{fig:overview}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{block-diagram.pdf}
  \caption{Block diagram of implementation}\label{fig:block-diagram}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{training_overview.pdf}
  \caption{Overview over our framework, showing blocks existing (black) and components currently worked on (gray).}\label{fig:overview}
\end{figure*}

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[width=\linewidth]{block-diagram.pdf}
  \caption{Block diagram of the implementation, On the left the host code, and on the right side the device code. The host side orchestrates all the computation on the device side.}\label{fig:block-diagram}
\end{figure*}
